---
title: "KNN ML Auto Insurance"
author: "Kevin Sun"
date: "5/3/2022"
output: rmarkdown::github_document
---

*KNN Model with Auto Insurance Data*

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message=FALSE)
```

Clear working memory

```{r}
rm(list=ls())
```


Fit a KNN model to the data from the Caravan auto insurance dataset using outcome Purchase and all of the other variables in the dataset as predictors.

```{r}
# Write your code here
library(class) # package for knn classifier
Insurance_Data <- read.csv("AutoInsurance.csv")
attach(Insurance_Data)
#quick summary of data
colnames(Insurance_Data)
# Data standardization and training for knn
standardized.X=scale(Insurance_Data[,-86])
test=1:1000

train.X=standardized.X[-test ,] # exclude test sample
test.X=standardized.X[test ,]

train.Y=Purchase[-test] # exclude test sample
test.Y=Purchase[test]
```

KNN model with K=2 with confusion matrix. Hypothetical success rate and profits

```{r}
#Set seed
set.seed(1) 
#Generate KNN model with K=2
nearest1_pred=knn(train = train.X, test= test.X, cl= train.Y,k=2)
# Confusion Matrix: Rate of Predicted vs Actual Values
table(nearest1_pred,test.Y)
#Success Rate
8/(8+58)
# random guess positive rate
(51+8)/1000
# Profits with marketing strategy suggested by KNN
-66*(180)+8*(1800)
# End of your code
```

KNN model with K=5 with confusion matrix. Hypothetical success rate and profits


```{r}
set.seed(1) # Set seed
#Generate KNN model with K=5
nearest1_pred=knn(train = train.X, test= test.X, cl= train.Y,k=5)
# Confusion Matrix: Rate of Predicted vs Actual Values
table(nearest1_pred,test.Y)
#Success Rate
4/(11+4)
# random guess positive rate
(55+4)/1000
# Profits with marketing strategy suggested by KNN
-15*(180)+4*(1800)
# End of your code
```

KNN model with K=10 with confusion matrix. Hypothetical success rates and profits.

```{r}
set.seed(1) # Set seed
#Generate KNN model with K=10
nearest1_pred=knn(train = train.X, test= test.X, cl= train.Y,k=10)
# Confusion Matrix: Rate of Predicted vs Actual Values
table(nearest1_pred,test.Y)
#Success Rate
1/(0+1)
# random guess positive rate
(58+1)/1000
# Profits with marketing strategy suggested by KNN
-1*(180)+1*(1800)
# End of your code
```


*Conclusion:* As k in the KNN increases, the success rate increases. This makes sense as increasing amount of nearest neighbors decreases variance, but also increases bias. There is a bias-variance tradeoff. However, profits do not necessarily increase and go up with k. Profits are higher when k=5 than k=2 or k=10 as the success rate is more optimal in both chance and quantity. Hence, it is best to balance the variance and bias, selecting an optimal amount of nearest neighbors that will maximize profit (e.g. k=5).
